%!TEX root = ./seminar.tex
\section{The Future of Digital Healthcare}
\subsection{Secure Management of Patient Data}
With the digitization of healthcare environments a lot of patient data must be stored and accessed by algorithms. While this in itself is of less concern, security measurements need to be taken to prevent unauthorized access to this data. In addition, countries like Germany take confidentiality and security of data seriously and therefore have very strict regulations regarding storage, usage and even collection of said data \cite{dsgvo}. Regardless of security concerns, the race for your data has already begun, with Apple releasing Apple Health Record and Apple Watch with a single-lead ECG \cite{appleHealth}. Joining Google with Google Fit and their WearOS - an operating system for smartwatches. Introducing Big Data concepts in the public healthcare sector may shift the focus from reactive to proactive care, reducing running costs and improving efficiency. This spans nearly all aspects of healthcare like diagnosis, treatment and population health management, to name a few. Furthermore, in moving from a volume-based to a value-based business model, healthcare providers see availability and accuracy of patients health data as pivotal. Now concerning security, healthcare data is stored in data centers with varying levels of security. They receive giant amounts of data from an even broader variety of sources. A first step to manage this data effectively and secure, is to introduce common data representations and local and regional standards. This allows the implementation of secure protocols for transportation and analysis in real-time. Currently, the healthcare industry is facing Distributed Denial of Service (DDoS) attacks, malware and social engineering attacks among others. As IoT environments are a big part of digital healthcare, their security is yet another problem, as implementing security in resource-constrained networks is an ever arising challenge. An approach would be to develop scaling key management solutions for secure transport of data in reasonable time-constraints. A last point that is key to patient privacy and data confidentiality is anonymization of data prior to anaytics \cite{patil2014big}.
\subsection{Individually Tailored Care}
\subsection{Smart Implants}
\subsection{Value-Based Healthcare}

